Testing Statistical Graphics

### 2022-06-26 index.qmd
Fix formatting
Add mahbub's arxiv paper about demographics

While studies have found some relationship between lineup performance and completion of calculus\cite{vanderplasSpatialReasoningData2016a}, these differences are relatively small. 
Studies have also not found a strong relationship between visual task performance and participant recruitment method\cite{vanderplasFramedReproducingRevisiting2019}, perhaps in part because demographics which use social media sites and demographics completing online research tasks for pay overlap heavily. 
What is clear, however, is that some participants are very good at evaluating graphics and some participants are not; as a result, it can be extremely helpful to use random effects models with an effect for individual participants.

@@

One highly useful (but not strictly essential) component of an experiment that can be set up during the pilot testing stage is a basic analysis script which summarizes all data collected to date visually. 
We have used such scripts in the past to produce automatically updating dashboards or web pages, allowing for real time or near-real time monitoring of data collection efforts. 
This provides an easy way to summarize completion of the experiment so that individuals can receive credit (if using services like MTurk or Prolific), but also allows interested participants to see the data if recruiting participants who are more likely to be interested in the results, as sometimes happens on social media sites. 
As data collection online can also happen extremely quickly (300 participants in <2h in our most recent Prolific experiment), this can provide an illusion of control over the deluge of data, allowing any issues to be spotted and resolved relatively quickly. 
If server load is a potential issue, it may also help to release batches of trials over a longer period of time in order to minimize the chance of having to make participants wait for others to complete the task before the server can handle additional connections^[This is the one major drawback to our preferred solution of self-hosting a Shiny server to handle data collection: the free version of Shiny server is limited to about 15 connections at any given time.]. 
\
# Analyzing the Data
Be prepared for surprises

>>>>

While studies have found some relationship between lineup performance and demographic factors\cite{majumderHumanFactorsInfluencing2014, vanderplasSpatialReasoningData2016a}, these differences are relatively small and unlikely to be important. 
Studies have also not found a strong relationship between visual task performance and participant recruitment method\cite{vanderplasFramedReproducingRevisiting2019}, perhaps in part because demographics which use social media sites and demographics completing online research tasks for pay overlap heavily. 
What is clear, however, is that some participants are very good at evaluating graphics and some participants are not; as a result, it can be extremely helpful to use random effects models with an effect for individual participants.

@@

One highly useful (but not strictly essential) component of an experiment that can be set up during the pilot testing stage is a basic analysis script which summarizes all data collected to date visually. 
We have used such scripts in the past to produce automatically updating dashboards or web pages, allowing for real time or near-real time monitoring of data collection efforts. 
This provides an easy way to summarize completion of the experiment so that individuals can receive credit (if using services like MTurk or Prolific), but also allows interested participants to see the data if recruiting participants who are more likely to be interested in the results, as sometimes happens on social media sites. 
As data collection online can also happen extremely quickly (300 participants in <2h in our most recent Prolific experiment), this can provide an illusion of control over the deluge of data, allowing any issues to be spotted and resolved relatively quickly. 
If server load is a potential issue, it may also help to release batches of trials over a longer period of time in order to minimize the chance of having to make participants wait for others to complete the task before the server can handle additional connections^[This is the one major drawback to our preferred solution of self-hosting a Shiny server to handle data collection: the free version of Shiny server is limited to about 15 connections at any given time.].

# Analyzing the Data

Be prepared for surprises
